Appendix for 'Framing Effects in the Wild

### 2022-08-24 paper/appendix.Rmd
Add LTP DiD and Change plot
Improve plot and variable description migration attitudes

@@

@@

@@

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(init_mig_groups != "", !is.na(`1130_clean`), !is.na(treat)) %>% 
  group_by(treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    `1130_clean` = mean(`1130_clean`, na.rm = T)
  ) %>% 
  ggplot(aes(x = date_clean, y = `1130_clean`, lty = !treat, col = !treat)) +
  geom_line() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  # facet_wrap(~init_mig_groups, ncol = 1) + 
  theme_minimal()

>>>>

# Change in Migration Attitudes across time

MigChangePlot()

[Add description of variable and explanation]

@@

## Effect in Longterm-Panel

### Reichelt

```{r LTPDiD, fig.height=2}

LTPDiD()

```{r LTPDiD_table}

LTPDiD(return_table = T)

@@

(1) Zuzug von Ausländern erleichtern
(2)
(3)
(4)
(5)
(6)
(7) Zuzug von Ausländern einschränken

@@

fread(here('data/raw/gles/Panel/long_cleaned.csv')) %>% 
  filter(!is.na(`1130_clean`), !is.na(treat)) %>% 
  group_by(treat, wave) %>% 
  summarise(
    date_clean = min(date_clean, na.rm = T),
    mig_mean = mean(`1130_clean`, na.rm = T),
    mig_sd = sd(`1130_clean`, na.rm = T),
    N = n()
  ) %>% 
  mutate(
    mig_lower = mig_mean + qt(0.025, df = N-1) * (mig_sd/sqrt(N)),
    mig_upper = mig_mean + qt(0.975, df = N-1) * (mig_sd/sqrt(N))
  ) %>% 
  ggplot(aes(x = date_clean, y = mig_mean,
             ymin = mig_lower, ymax = mig_upper,
             lty = !treat, col = !treat)) +
  geom_line() +
  geom_pointrange() +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") + 
  theme_minimal() +
  labs( x = "", y = "", col = "Readership", lty = "Readership") +
  scale_color_manual(labels = c("Bild", "Never Bild"),
                     values = MetBrewer::met.brewer("Archambault", 2)) +
  scale_linetype_manual(labels = c("Bild", "Never Bild"),
                     values = c(1,2))
